%-------------------------
% Resume in Latex
% Author : Diego Renner
% Based on: Sourabh Bajaj repo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{lmodern}
\usepackage{anyfontsize}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{plain}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands
\newcommand{\resumeItem}[1]{%2
\item\small{
		%\textbf{#1}
		#1
		%{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{8pt}\item%-1
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
	\vspace{1pt}
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
	\textbf{#1:} #2
}

% COLOR THEMES SELECTION
% For Light theme un-comment this and comment the Dark theme section below
% \colorlet{urlcolor}{blue}
% \newcommand{\otherThemeRef}{\href{https://github.com/DiegoRenner/CV/blob/master/CV_dark.pdf}{See dark theme}}
% \newcommand{\latestVersion}{\href{https://github.com/DiegoRenner/CV/blob/master/CV_light.pdf}{Get Latest version}}

\input{\jobname.theme}
% For Dark theme un-comment this and comment the Light theme section above

%\colorlet{textcolor}{white!80!gray}
%\colorlet{backgroundcolor}{black!30!gray}
%\colorlet{urlcolor}{blue!25!white}
%\AtBeginDocument{\color{textcolor}}
%\newcommand{\otherThemeRef}{\href{https://github.com/DiegoRenner/CV/blob/master/CV_light.pdf}{See light theme}}
%\newcommand{\latestVersion}{\href{https://github.com/DiegoRenner/CV/blob/master/CV_dark.pdf}{Get Latest version}}
% ---

% DOCUMENT MAIN
\begin{document}


% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://www.linkedin.com/in/diego-renner-6169851b5/}{\Large Diego Renner}} &  \href{https://github.com/DiegoRenner}{ \faicon{github} \color{urlcolor} DiegoRenner} \\
	\href{mailto:diego.renner@sam.math.ethz.ch}{diego.renner@sam.math.ethz.ch} &  \faicon{code} C++, Python, Java\\
	\textsl{\small \latestVersion} & \textsl{\small \otherThemeRef}
\end{tabular*}
% ---

% EXPERIENCE
\section{Experience}
\resumeSubHeadingListStart


\resumeSubheading
{ETH Zürich}{Zurich, Switzerland}
{Teaching Assistant}{Sepember 2021 - February 2022}
\resumeItemListStart
\resumeItem{Teaching Assistant for Lecture "Numerical Methods for Computer Science".}
\resumeItemListEnd
\resumeTech{Technologies}{C++}\\
\resumeTech{Theory}{ODEs, PDEs and numerical algorithms to solve them.}

\resumeSubheading
{ETH Zürich}{Zurich, Switzerland}
{Research Assistant}{September 2020 - June 2021}
\resumeItemListStart
\resumeItem{Hired for continued development of BEM code that was implemented in Masters Thesis.}
\resumeItemListEnd
\resumeTech{Technologies}{C++, CMake, Git}\\
\resumeTech{Theory}{BEM, Resonances in Transmission Scattering Problems}

\resumeSubheading
{ETH Zürich}{Zurich, Switzerland}
{Teaching Assistant}{September 2020 - February 2021}
\resumeItemListStart
\resumeItem{Teaching Assistant for Lecture "Numerical Methods".}
\resumeItemListEnd
\resumeTech{Technologies}{C++, CMake}\\
\resumeTech{Theory}{ODEs, PDEs and numerical algorithms to solve them.}

\resumeSubheading
{CSCS Swiss National Supercomputing Center}{Lugano, Switzerland}
{Internship}{May 2018 - August 2018}
\resumeItemListStart
\resumeItem{Writing regression checks for Piz Daint, Cray XC40/XC50 production system.}
\resumeItemListEnd
\resumeTech{Technologies}{C, MPI, MySQL, Kibana, Grafana}\\
%
%\resumeSubheading
%{Coople}{Basel/Zurich, Switzerland}
%{Logistics \& Service}{2013 - 2020}
%\resumeItemListStart
%\resumeItem{50+ employments at events and meetings.}
%\resumeItem{Favoured by 8 employers on the jobs distribution platform Coople due to reliability and efficiency.}
%\resumeItemListEnd
%%\newpage
%
%\resumeSubheading
%{Eugen Leu \& Partner AG, Photography Studio}{Riehen, Switzerland}
%{Internship}{September 2011 - October 2011}
%\resumeItemListStart
%\resumeItem{Preparing photosets and learning professional workflows.}
%\resumeItemListEnd
\resumeSubHeadingListEnd
%% ---
%
% EDUCATION
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{ETH Zürich}{Zurich, Switzerland}
{M.Sc. Maths}{September 2021 - December 2023}
\resumeItemListStart
\resumeItem{Strengthened analytical abilities in pure maths courses and coding skills in thesis on differentiable haemodynamics solver (Python).}
\resumeItemListEnd
\resumeSubheading
{ETH Zürich}{Zurich, Switzerland}
{M.Sc. Computational Science and Engineering, Specialization Physics}{September 2018 - August 2021}
\resumeItemListStart
\resumeItem{Degree completed with a thesis on solving the transmission scattering problem using BEM (C++).}
\resumeItemListEnd
\resumeSubheading
{Universität Basel}{Basel, Switzerland}
{B.Sc. Computational Mathematics}{September 2014 - Februar 2018}
\resumeItemListStart
\resumeItem{Completed extracurricular courses on Computer Architecture, Operating Systems and Quantum Mechanics.}
\resumeItemListEnd
\resumeSubheading
{Gymnasium Bäumlihof}{Basel, Switzerland}
{Matura, Specialization Biology \& Chemistry}{August 2009 - July 2014}
\resumeSubHeadingListEnd
% ---


\section{Certificates \& Extracurriculars}
\resumeSubHeadingListStart
\resumeSubheading
{Ready, set, go! A short introduction for Student
Teaching Assistants}{(remote) Zurich}
{Education Development and Technology, ETH Zurich}{April 2020}
\resumeItemListStart
\resumeItem{Improving didactic skills}
\resumeItem{Setting goals for upcoming teaching activity}
\resumeItemListEnd
\resumeSubheading
{Effective High-Performance Computing \& Data Analytics with GPU}{(remote) Lugano, Switzerland}
{Summerschool, CSCS-USI}{July 2020}
\resumeItemListStart
\resumeItem{GPU: architecture \& programming (CUDA, OpenACC)}
\resumeItem{JupyterLab}
\resumeItem{Python: Numpy, SciPy, Dask, Numba}
\resumeItem{ML: Rapids}
\resumeItem{Deep Learning: TensorFlow}
\resumeItemListEnd
\resumeSubheading
{International Consulting Network (ICON)}{Shanghai, (remote) Belo Horizonte}
{Student Consulting Network}{March 2017 - Februar 2018}
\resumeItemListStart
\resumeItem{Market Research \& Trend Analysis}
\resumeItem{Consulting for CREP (Real Estate, China) \& Lalubema (Private Security, Brazil)}
\resumeItemListEnd
\resumeSubHeadingListEnd

% ---
\hfill \textsl{Following sections items are clickable}


% PROJECTS
\section{Projects \& Thesis}

\resumeSubHeadingListStart
\resumeSubItem{\href{https://github.com/ktrianta/n-body-problem}{Parallelizing the Barnes-Hut Algorithm with MPI: Parallelized implementation of N-Body solver in C++ using the MPI framework. (Course Work)}}

\resumeSubItem{\href{https://github.com/DiegoRenner/phonons}{AiiDA Lab implementation of IR spectrum calculations for carbon based nanomaterials: An AiiDa workflow implemented in the Jupyter Notebooks based AiiDa lab interface. (Semesters Thesis, Computational Science)}}

\resumeSubItem{\href{https://github.com/DiegoRenner/HelmholtzTransmissionProblemBEM}{Near Resonances for Scattering Transmission Problems: A BEM based C++ solver for Scattering Transmission Problems, developed to investigate scatterer-dependent near resonances. (Masters Thesis, Computational Science)}}

\resumeSubItem{\href{https://www.researchgate.net/publication/372765555_Detecting_Near_Resonances_in_Acoustic_Scattering}{Detecting Near Resonances in Acoustic Scattering: Continued development of root finding algorithm from the masters thesis using empirical evidence and state of the art computation of singular values. (Published Paper)}}

\resumeSubItem{\href{https://github.com/DiegoRenner/Game-Sim-ML-in-Finances-}{ML based game simulation in a finance setting: Agents trained to trade or hold a stock taking into account real historical data on cash returns. Policies are learned via reinforcement learning. (Course Work)}}

\resumeSubItem{\href{https://github.com/DiegoRenner/jaxFlowSim}{On differentiable simulations of haemodynamic systems: A 1D-haemodynamics solver written in Python using JAX. The differentiability of the solver aims to aid in the development of personalised medicine. (Masters Thesis, Maths)}}

\resumeSubHeadingListEnd
% ---
\end{document}
